Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-17 writeup/gz_hubble_data.tex
Changed all HST curves to system throughput

\documentclass[twocolumn]{aastex}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
unfilled black curves show the filters for the Suprime Camera on the
\textit{Subaru} telescope, which was used to create color gradients in the GZH
images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

The properties of the individual surveys are as follows:

@@

\begin{table*}
\center
\caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lllcrr}
\hline\hline
Survey &  Total $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                                   & 2100$-$2300  & \Vband, \Iband{}                 & 0.03 & 710                & 8157    \\
COSMOS                                  & 2028         & \Iband{}                         & 0.05 & 6480               & 88530   \\
GEMS                                    & 2160$-$2286  & \Vband, \zband{}                 & 0.03 & 800                & 9143    \\
GOODS                                   & $-$          & $-$                              & $-$  & $-$                & $-$     \\
\hspace{10pt} \emph{GOODS-N~2~epoch}    & 2100$-$4200  & \Vband, \iband                   & 0.03 & 320                & 2551    \\
\hspace{10pt} \emph{GOODS-S~2~epoch}    & 2100$-$4200  & \Vband, \zband                   & 0.03 & 320                & 3593    \\
\hspace{10pt} \emph{GOODS-N~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 6015    \\
\hspace{10pt} \emph{GOODS-S~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 5142    \\
\hline
total                                   & $-$          & $-$                              & $-$  & 8630 & 123131  \\
\hline\hline
\end{tabular}
\end{table*}

@@

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by combining stars in the GOODS fields using the PSF creation tools in \texttt{daophot}. 
The second set (version~2) was assembled from 96~galaxies in GOODS-S; this
version used simulated PSFs from \texttt{TinyTim} \citep{kri93}, drizzled using the same procedures as those used in reduction of the GOODS-S images \citep{koe02,koe03,gia04}. The use of these 2 versions facilitates comparisons between these different PSF creation methods, which are widely used in AGN host galaxy morphology studies \citep[e.g.,][]{san04,sim08,pie10a,simm11}. 
% okay so I'm a cheeky self-citing biyotch
Each PSF creation method has advantages and disadvantages: the empirical PSFs better represent the nuances of the PSF in the specific data being used and look more realistic at lower luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs are visually more realistic at higher luminosities.

Images with simulated AGN were classified in the main interface in an identical
manner and evenly distributed with unaltered images of the galaxies.
Classifiers were not explicitly told that the images had been altered during classification, as the
goal was to measure the effect on normal classifications in as unbiased a
manner as possible. Following classification, a classifier could view a page with additional details about each galaxy they had classified; where applicable these pages contained further information regarding image modifications.

@@

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
priority is spectroscopic redshifts; these were taken from the ACS-GC
\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
high-quality spectroscopic redshift in the ACS-GC is the primary option; if
none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
than 98\% are consistent at $\Delta z<0.001$, and so the order of selection
made no practical difference. Those which are inconsistent ($\Delta z>0.001$) between any of the three catalogs are marked with a Boolean flag in the column $\tt z\_spec\_conflict\_flag$ in Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were available,
the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
redshift with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.

@@

Below we describe the classification structure of GZH, including the software 
interface and the hierarchical structure of a classification. Section \ref{ssec:weighting}
describes the process of combining individual classifications into vote fractions for each
galaxy.

@@

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
simulated AGN were activated in Dec 2010, as well as a small sample of
images from AEGIS, GEMS, and GOODS that were previously excluded from the original sample
due to cuts on blended and/or saturated objects and subsequently confirmed as classifiable galaxies. The main GZH
site collected data until its replacement, the fourth phase of
Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on
the fourth version of the Galaxy~Zoo site. The GZH project had a total of
10,349,357~classifications from 93,898 registered participants. 
% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

As a first step to producing consensus classifications of each galaxy, 
the votes of individual classifiers in GZH were combined to make a vote
fraction for each response ($f_{response}$) to a question in the classification
tree. Votes were subsequently weighted and re-combined in an iterative method similar that in 
previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a method chosen 
to be as egalitarian as possible while also identifying and downweighting classifiers 
who frequently disagreed with others. The weighting factor $(w)$ was 1 for the
top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
classifiers, $w$ was designed to drop smoothly and was effectively zero for the
bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
% would be good to quantify "tiny" and "even smaller [than tiny]"
an even smaller percentage of the classifications) the overall effect on the
GZH dataset was minimal. The method was effective, however, at filtering out
contributions from random or deliberately malicious classifiers.

Classifications were aggregated and weighted only if the classifier was logged
into GZH under their username (which was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous'' and assumed to have $w = 1$. 
% We should also try to estimate how many anonymous classifiers there were, if possible.

>>>>

\documentclass[twocolumn]{aastex6}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{System throughput (fractional photon detection efficiency) of the
filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel
mode for the various surveys in GZH. The unfilled black curves show the filters
for the Suprime Camera on the \textit{Subaru} telescope, which was used to
create color gradients in the GZH images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

@@

\begin{table*}
\center
\caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                                   & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                                  & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                                    & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                                   & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   &   \\
\hspace{10pt} \emph{GOODS-N~2~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S~2~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{3593}  \\
\hspace{10pt} \emph{GOODS-N~5~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{6015}  \\
\hspace{10pt} \emph{GOODS-S~5~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{5142}  \\

\hline
total                                   & $-$         & $-$                              & $-$  & 8310  & 130467  \\
\hline\hline
\end{tabular}
\end{table*}

@@

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}.
The second set (version~2) was assembled from 96~galaxies in GOODS-S; this
version used deeper imaging and improved PSFs from \texttt{TinyTim}.

Images with simulated AGN were classified in the main interface in an identical
manner and evenly distributed with unaltered images of the galaxies.
Classifiers were not explicitly told that the images had been altered, as the
goal was to measure the effect on normal classifications in as unbiased a
manner as possible.

@@

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
priority is spectroscopic redshifts; these were taken from the ACS-GC
\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
high-quality spectroscopic redshift in the ACS-GC is the primary option; if
none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
than 98\% are consistent ($\Delta z<0.001$), and so the order of selection
made no practical difference. Galaxies with inconsistent spectroscopic
redshifts between any pair of catalogs are marked with a flag in
Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were available, the
1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
redshift with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.

@@

The votes of individual classifiers in GZH were combined to make a vote
fraction for each response ($f_{response}$) to a question in the classification
tree. Votes were weighted in a method similar that in previous versions of
Galaxy~Zoo \citep{lan08,wil13}, such that classifiers who frequently disagreed
with others ended up having very low weights. The weighting $(w)$ was 1 for the
top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
classifiers, $w$ was designed to drop smoothly and was effectively zero for the
bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
an even smaller percentage of the classifications) the overall effect on the
GZH dataset was minimal. The method was effective, however, at filtering out
contributions from random or deliberately malicious classifiers.

Classifications were aggregated and weighted only if the classifier was logged
into GZH under their username (which was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous''; no weighting was applied, but the data were otherwise treated
identically in the data processing.

@@

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
simulated AGN were activated in Dec 2010, as well as a small sample of
AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on
an overly restrictive cut on blended and/or saturated objects. The main GZH
site collected data until its replacement, the fourth phase of
Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on
the fourth version of the Galaxy~Zoo site. The GZH project had a total of
10,349,357~classifications from 93,898 registered participants. 
% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.
